---
layout: single
lang: en
categories: data
tags: dplyr
classes: wide
---

```{r setup}

```

### Video tutorials on dplyr

[Michael Chow | Bringing the Tidyverse to Python with Siuba](https://www.youtube.com/watch?v=w4Mi0u4urbQ)
[Hadley Wickham's "dplyr" tutorial at useR 2014 (1/2)](https://www.youtube.com/watch?v=w4Mi0u4urbQ)


Notes:
- Headley 2014 Talk figure on think -> code -> do process (There is a cognitive aspect of the first stage. That journey is easened by dplyr's grammar)
- Five key verbs of dplyr: (1) filter (2) select (3) mutate (4) summarise (5) arrange + group_by
- pipe %>% f(x,y) = x %>% y
- There are other verbs as well:
    - Rows:
filter() chooses rows based on column values.
slice() chooses rows based on location.
arrange() changes the order of the rows.
    - Columns:
select() changes whether or not a column is included.
rename() changes the name of columns.
mutate() changes the values of columns and creates new columns.
relocate() changes the order of the columns.
    - Groups of rows:
summarise() collapses a group into a single row.


```{r}
library(tidyverse)
?dplyr()
options(browser = "qutebrowser")
browseVignettes(package = "dplyr")
```




